04-Data-Analysis

### 2021-04-21 00-Data-Processing/04-Data-Analysis.Rmd
Add population output
Clean up pre-processing code and add output by population groups from tts

Invoke data:
```{r}
load("output-data-files/data_da_2016.RData")
load("output-data-files/dwelling_network_points_2016.RData")
load("output-data-files/hamilton_cma.RData")
load("output-data-files/foodbank_locations.RData")
load("output-data-files/modes_less40k.RData")
load("output-data-files/ttm_car.RData")
load("output-data-files/ttm_transit.RData")
load("output-data-files/ttm_walk.RData")
#data("data_da_2016")
#data("dwelling_network_points_2016")
#data("hamilton_cma")
#data("modes_less40k")
#data("foodbank_locations")
#data("ttm_car")
#data("ttm_transit")
#data("ttm_walk")
```

## TEMP: REMOVE INAPPLICABLE DESTINATIONS UNTIL NEW TTMs ARE FINISHED

```{r}
ttm_car <- ttm_car %>%
  filter(!between(OBJECTID, left = 59, right = 69))

ttm_transit <- ttm_transit %>%
  filter(!between(OBJECTID, left = 59, right = 69))

ttm_walk <- ttm_walk %>%
  filter(!between(OBJECTID, left = 59, right = 69))
```

@@

Join number of low income households per DA to dwellings and total number of residential units:
```{r}
dwelling_network_points_2016 <- dwelling_network_points_2016 %>%
  left_join(data_da_2016 %>%
              st_drop_geometry() %>%
              dplyr::transmute(DAUID = GeoUID, 
                               p_inc_less40k,
                               linc_age_0to2,
                               linc_age_0to19,
                               linc_age_65plus),
            by = "DAUID")
```

Calculate probability that a point on the network will have low income households. This is the proportion of low income households in the DA multiplied by the total number of residential units a the point:
```{r}
dwelling_network_points_2016 <- dwelling_network_points_2016 %>%
  mutate(income_less40k = p_inc_less40k * Dwellings)
```

Join the household data to the travel time matrices:
```{r}
ttm_car <- ttm_car %>%
  left_join(dwelling_network_points_2016 %>%
              st_drop_geometry() %>%
              dplyr::select(ID, 
                            income_less40k,
                            linc_age_0to2,
                            linc_age_0to19,
                            linc_age_65plus,
                            DAUID, 
                            TAZUID),
            by = c("UID" = "ID"))

ttm_transit <- ttm_transit %>%
  left_join(dwelling_network_points_2016 %>%
              st_drop_geometry() %>%
              dplyr::select(ID, 
                            income_less40k,
                            linc_age_0to2,
                            linc_age_0to19,
                            linc_age_65plus,
                            DAUID, 
                            TAZUID),
            by = c("UID" = "ID"))

ttm_walk <- ttm_walk %>%
  left_join(dwelling_network_points_2016 %>%
              st_drop_geometry() %>%
              dplyr::select(ID, 
                            income_less40k,
                            linc_age_0to2,
                            linc_age_0to19,
                            linc_age_65plus,
                            DAUID, 
                            TAZUID),
            by = c("UID" = "ID"))
```

@@

Join tables:
```{r}
ttm <- ttm_car %>%
  rename(travel_time_car = travel_time) %>%
  full_join(ttm_transit %>%
              transmute(UID,
                        OBJECTID,
                        travel_time_transit = travel_time),
            by = c("UID", "OBJECTID")) %>%
  full_join(ttm_walk %>%
              transmute(UID,
                        OBJECTID,
                        travel_time_walk = travel_time),
            by = c("UID", "OBJECTID"))
```

Join proportion of trips to travel time table:
```{r}
ttm <- ttm %>%
  left_join(modes %>%
              st_drop_geometry() %>%
              transmute(TAZUID,
                        p_car,
                        p_transit,
                        p_walk),
            by = "TAZUID")
```

@@

Plot:
```{r}
ggplot() +
  geom_sf(data = hamilton_cma) +
  geom_sf(data = e_travel_time_parcel,
          aes(color = e_travel_time),
          alpha = 0.3) + 
  scale_color_distiller(palette = "OrRd", direction = 1)
```

@@

Plot:
```{r}
ggplot() +
  geom_sf(data = hamilton_cma) +
  geom_sf(data = e_travel_time_parcel_2,
          aes(color = e_travel_time),
          alpha = 0.3) + 
  scale_color_distiller(palette = "OrRd", direction = 1)
```

@@

Plot levels of service before and during covid:
```{r}
los_pre <- ggplot() +
  geom_sf(data = hamilton_cma) +
  geom_sf(data = los %>%
            filter(timing == "Pre-covid"),
          aes(color = los,
              size = los)) +
  geom_sf(data = foodbank_locations,
          aes(shape = COVIDClose)) +
  scale_color_distiller(palette = "OrRd", 
                        direction = 1) +
  scale_shape_manual(values = c("Yes" = 4, "No" = 1))

los_covid <- ggplot() +
  geom_sf(data = hamilton_cma) +
  geom_sf(data = los %>%
            filter(timing == "During covid"),
          aes(color = los,
              size = los)) +
  geom_sf(data = foodbank_locations,
          aes(shape = COVIDClose)) +
  scale_color_distiller(palette = "OrRd", 
                        direction = 1) +
  scale_shape_manual(values = c("Yes" = 4, "No" = 1))

@@

Plot the change in level of service:
```{r}
los %>%
  st_drop_geometry() %>%
  pivot_wider(names_from = timing, 
              values_from = los, 
              values_fill = 0) %>%
  filter(`During covid` > 0) %>%
  mutate(los_d = `During covid` / `Pre-covid` - 1) %>%
  left_join(foodbank_locations %>%
            transmute(OBJECTID = ID,
                      geometry),
          by = "OBJECTID") %>%
  st_as_sf() %>%
  ggplot() +
  geom_sf(data = hamilton_cma) +
  geom_sf(aes(color = los_d,
              size = los_d)) +
  geom_sf(data = foodbank_locations,
          aes(shape = COVIDClose)) +
  scale_color_distiller(palette = "OrRd", 
                        direction = -1) +
  scale_shape_manual(values = c("Yes" = 4, "No" = 1))

@@

Plot accessibility before and during covid:
```{r}
acc_pre <- ggplot() +
  geom_sf(data = hamilton_cma) +
  geom_sf(data = accessibility %>%
            filter(timing == "Pre-covid"),
          aes(color = accessibility)) +
  scale_color_distiller(palette = "OrRd", 
                        direction = 1)

acc_covid <- ggplot() +
  geom_sf(data = hamilton_cma) +
  geom_sf(data = accessibility %>%
            filter(timing == "During covid"),
          aes(color = accessibility)) +
  scale_color_distiller(palette = "OrRd", 
                        direction = 1)

@@

Plot the change in accessibility by DA:
```{r}
accessibility %>%
  st_drop_geometry() %>%
  # Copy the DA identifier to the accessibility table
  left_join(dwelling_network_points_2016 %>%
              st_drop_geometry() %>%
              transmute(UID = ID, DAUID),
            by = "UID") %>%
  # Group by DA and time
  group_by(DAUID, timing) %>%
  # Calculate the accessibility by DA before and during covid
  summarize(accessibility = sum(accessibility),
            timing = first(timing),
            .groups = "drop") %>%
  # Pivot wider to calculate the differences in accessibility from pre-covid to covid
  pivot_wider(names_from = timing, 
              values_from = accessibility) %>%
  # Calculate changes in accessibility
  mutate(acc_d = `During covid` / `Pre-covid` - 1) %>%
  # Join DA geometry
  left_join(data_da_2016 %>%
            transmute(DAUID = GeoUID,
                      geometry),
          by = "DAUID") %>%
  # Convert to simple features
  st_as_sf() %>%
  # Plot
  ggplot() +
  geom_sf(data = hamilton_cma) +
  geom_sf(aes(fill = acc_d),
          color = NA) +
  scale_fill_distiller(palette = "OrRd", 
                        direction = -1)

@@

### CODE TO BE UPDATED
```{r}
# join tripmaking modal proportions
ttm_car <- ttm_car %>%
  left_join(modes %>%
              st_drop_geometry() %>%
              transmute(TAZUID,
                        p_car,
                        p_transit,
                        p_walk),
            by = "TAZUID")

@@

```{r minimum-travel-time-baseline, include=FALSE}
# retrieve minimum travel time during covid to sites that didnt close
min_ttm_car_pre <- ttm_car %>%
  #dplyr::filter(COVIDClose == "No") %>%
  group_by(UID) %>%
  summarize(travel_time = min(travel_time),
            linc_age_0to2 = first(linc_age_0to2),
            linc_age_0to19 = first(linc_age_0to19),
            linc_age_65plus = first(linc_age_0to19),
            DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            p_car = first(p_car),
            p_transit = first(p_transit),
            p_walk = first(p_walk),
            .groups = "drop")

min_ttm_transit_pre <- ttm_transit %>%
  #dplyr::filter(COVIDClose == "No") %>%
  group_by(UID) %>%
  summarize(travel_time = min(travel_time),
            linc_age_0to2 = first(linc_age_0to2),
            linc_age_0to19 = first(linc_age_0to19),
            linc_age_65plus = first(linc_age_0to19),
            DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            p_car = first(p_car),
            p_transit = first(p_transit),
            p_walk = first(p_walk),
            .groups = "drop")

min_ttm_walk_pre <- ttm_walk %>%
  #dplyr::filter(COVIDClose == "No") %>%
  group_by(UID) %>%
  summarize(travel_time = min(travel_time),
            linc_age_0to2 = first(linc_age_0to2),
            linc_age_0to19 = first(linc_age_0to19),
            linc_age_65plus = first(linc_age_0to19),
            DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            p_car = first(p_car),
            p_transit = first(p_transit),
            p_walk = first(p_walk),
            .groups = "drop")
```

Get minimum travel times in the during covid scenario:

```{r minimum-travel-time-during-covid, include=FALSE}
# retrieve minimum travel time during covid to sites that didnt close
min_ttm_car_during <- ttm_car %>%
  dplyr::filter(COVIDClose == "No") %>%
  group_by(UID) %>%
  summarize(travel_time = min(travel_time),
            linc_age_0to2 = first(linc_age_0to2),
            linc_age_0to19 = first(linc_age_0to19),
            linc_age_65plus = first(linc_age_0to19),
            DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            p_car = first(p_car),
            p_transit = first(p_transit),
            p_walk = first(p_walk),
            .groups = "drop")

min_ttm_transit_during <- ttm_transit %>%
  dplyr::filter(COVIDClose == "No") %>%
  group_by(UID) %>%
  summarize(travel_time = min(travel_time),
            linc_age_0to2 = first(linc_age_0to2),
            linc_age_0to19 = first(linc_age_0to19),
            linc_age_65plus = first(linc_age_0to19),
            DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            p_car = first(p_car),
            p_transit = first(p_transit),
            p_walk = first(p_walk),
            .groups = "drop")

min_ttm_walk_during <- ttm_walk %>%
  dplyr::filter(COVIDClose == "No") %>%
  group_by(UID) %>%
  summarize(travel_time = min(travel_time),
            linc_age_0to2 = first(linc_age_0to2),
            linc_age_0to19 = first(linc_age_0to19),
            linc_age_65plus = first(linc_age_0to19),
            DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            p_car = first(p_car),
            p_transit = first(p_transit),
            p_walk = first(p_walk),
            .groups = "drop")
```

```{r}
# FULL JOIN THEM TOGETHER
```

## Exploratory data analysis

Summary of population:
```{r}
sum(data_da_2016$Population_55to69, na.rm = TRUE)
sum(data_da_2016$Population_70plus, na.rm = TRUE)
```

Check the total population:
```{r}
sum(dwelling_network_points_2016$Population_55to69, na.rm = TRUE)
sum(dwelling_network_points_2016$Population_70plus, na.rm = TRUE)
```

The difference in population is because the residential units considered do not completely cover the Hamilton CMA:
```{r}
ggplot() +
geom_sf(data = hamilton_cma) + 
geom_sf(data = dwelling_network_points_2016) + 
geom_sf(data = pharmacy_locations, 
aes(color = Type,
shape = Type), 
size = 3)
```

Plot population age 55 to 69:
```{r}
ggplot() +
geom_sf(data = data_da_2016 %>%
filter(`Region Name` == "Hamilton"),
aes(fill = Population_55to69),
color = NA) +
geom_sf(data = hamilton_cma,
fill = NA) +
scale_fill_distiller(palette = "OrRd", 
direction = 1)
```

Plot population age 70 plus:
```{r}
ggplot() +
geom_sf(data = data_da_2016 %>%
filter(`Region Name` == "Hamilton"),
aes(fill = Population_70plus),
color = NA) +
geom_sf(data = hamilton_cma,
fill = NA) +
scale_fill_distiller(palette = "OrRd", 
direction = 1)
```

>>>>

Invoke data:
```{r}
load("output-data-files/data_da_2016.RData")
load("output-data-files/dwelling_network_points_2016.RData")
load("output-data-files/hamilton_boundary.RData")
load("output-data-files/population_age_income.RData")
load("output-data-files/foodbank_locations.RData")
load("output-data-files/modes_less40k.RData")
load("output-data-files/ttm_car.RData")
load("output-data-files/ttm_transit.RData")
load("output-data-files/ttm_walk.RData")
#data("data_da_2016")
#data("dwelling_network_points_2016")
#data("hamilton_cma")
#data("modes_less40k")
#data("foodbank_locations")
#data("ttm_car")
#data("ttm_transit")
#data("ttm_walk")
```

## Remove entries in travel time matrices for inapplicable destinations

As a first step, we will remove the computed travel times to the three Community Kitchen locations (IDs 1-3):
```{r}
ttm_car <- ttm_car %>%
  filter(!between(OBJECTID, left = 1, right = 3))

ttm_transit <- ttm_transit %>%
  filter(!between(OBJECTID, left = 1, right = 3))

ttm_walk <- ttm_walk %>%
  filter(!between(OBJECTID, left = 1, right = 3))
```

@@

Join number of low income households per DA to dwellings and total number of residential units:
```{r}
dwelling_network_points_2016 <- dwelling_network_points_2016 %>%
  left_join(data_da_2016 %>%
              st_drop_geometry() %>%
              dplyr::transmute(DAUID = GeoUID, 
                               p_inc_less40k),
            by = "DAUID")
```

Calculate probability that a point on the network will have low income households. This is the proportion of low income households in the DA multiplied by the total number of residential units at the point:
```{r}
dwelling_network_points_2016 <- dwelling_network_points_2016 %>%
  mutate(income_less40k = p_inc_less40k * Dwellings)
```

Join the household data to the travel time matrices:
```{r}
ttm_car <- ttm_car %>%
  left_join(dwelling_network_points_2016 %>%
              st_drop_geometry() %>%
              dplyr::select(ID, 
                            income_less40k,
                            DAUID, 
                            TAZUID),
            by = c("UID" = "ID"))

ttm_transit <- ttm_transit %>%
  left_join(dwelling_network_points_2016 %>%
              st_drop_geometry() %>%
              dplyr::select(ID, 
                            income_less40k,
                            DAUID, 
                            TAZUID),
            by = c("UID" = "ID"))

ttm_walk <- ttm_walk %>%
  left_join(dwelling_network_points_2016 %>%
              st_drop_geometry() %>%
              dplyr::select(ID, 
                            income_less40k,
                            DAUID, 
                            TAZUID),
            by = c("UID" = "ID"))
```

@@

```{r}
# join tripmaking modal proportions
ttm_car <- ttm_car %>%
  left_join(modes %>%
              st_drop_geometry() %>%
              transmute(TAZUID,
                        p_car,
                        p_transit,
                        p_walk),
            by = "TAZUID")

Prepare and join population data:
```{r number-of-residential-units-per-DA, include=FALSE}
# Data preparation
## Find number of residential units in each DA. This is needed to assign the population to parcels
residential_units <- dwelling_network_points_2016 %>%
  st_drop_geometry() %>%
  group_by(TAZUID) %>%
  summarize(residential_units = sum(Dwellings))
```

```{r join-population-to-parcels, include=FALSE}
# Data preparation
## Join number of people age 55+ per DA to dwellings and total number of residential units:
dwelling_network_points_2016 <- dwelling_network_points_2016 %>%
  left_join(population_age_income %>%
              st_drop_geometry() %>%
              dplyr::transmute(TAZUID,
                               children,
                               adults,
                               seniors),
            by = "TAZUID") %>%
  left_join(residential_units,
            by = "TAZUID")
```

```{r calculate-population-per-parcel, include=FALSE}
# Data preparation
##Calculate population per point on the network. This is the population in the DA divided by the total number of residential units. This gives the average number of people per residential unit. Then, multiply by the number of dwellings (residential units) at the point:
dwelling_network_points_2016 <- dwelling_network_points_2016 %>%
  mutate(children = (children/residential_units) * Dwellings,
         adults = (adults/residential_units) * Dwellings,
         seniors = (seniors/residential_units) * Dwellings)
```

```{r join-population-data-to-travel-time-tables, include=FALSE}
# Data preparation
## Join the population data to the travel time matrices:
ttm_car <- ttm_car %>%
  left_join(dwelling_network_points_2016 %>%
              st_drop_geometry() %>%
              dplyr::transmute(ID, 
                            children,
                            adults,
                            seniors),
            by = c("UID" = "ID"))

ttm_transit <- ttm_transit %>%
  left_join(dwelling_network_points_2016 %>%
              st_drop_geometry() %>%
              dplyr::transmute(ID, 
                            children,
                            adults,
                            seniors),
            by = c("UID" = "ID"))

ttm_walk <- ttm_walk %>%
  left_join(dwelling_network_points_2016 %>%
              st_drop_geometry() %>%
              dplyr::transmute(ID, 
                            children,
                            adults,
                            seniors),
            by = c("UID" = "ID"))
```

Join all tables:
```{r}
ttm <- ttm_car %>%
  rename(travel_time_car = travel_time) %>%
  full_join(ttm_transit %>%
              transmute(UID,
                        OBJECTID,
                        travel_time_transit = travel_time),
            by = c("UID", "OBJECTID")) %>%
  full_join(ttm_walk %>%
              transmute(UID,
                        OBJECTID,
                        travel_time_walk = travel_time),
            by = c("UID", "OBJECTID"))
```

@@

Plot:
```{r}
ggplot() +
  geom_sf(data = hamilton_boundary) +
  geom_sf(data = e_travel_time_parcel,
          aes(color = e_travel_time),
          alpha = 0.3) + 
  scale_color_distiller(palette = "OrRd", direction = 1)
```

@@

Plot:
```{r}
ggplot() +
  geom_sf(data = hamilton_boundary) +
  geom_sf(data = e_travel_time_parcel_2,
          aes(color = e_travel_time),
          alpha = 0.3) + 
  scale_color_distiller(palette = "OrRd", direction = 1)
```

@@

Plot levels of service before and during covid:
```{r}
los_pre <- ggplot() +
  geom_sf(data = hamilton_boundary) +
  geom_sf(data = los %>%
            filter(timing == "Pre-covid"),
          aes(color = los,
              size = los)) +
  geom_sf(data = foodbank_locations,
          aes(shape = COVIDClose)) +
  scale_color_distiller(palette = "OrRd", 
                        direction = 1) +
  scale_shape_manual(values = c("Yes" = 4, "No" = 1))

los_covid <- ggplot() +
  geom_sf(data = hamilton_boundary) +
  geom_sf(data = los %>%
            filter(timing == "During covid"),
          aes(color = los,
              size = los)) +
  geom_sf(data = foodbank_locations,
          aes(shape = COVIDClose)) +
  scale_color_distiller(palette = "OrRd", 
                        direction = 1) +
  scale_shape_manual(values = c("Yes" = 4, "No" = 1))

@@

Plot the change in level of service:
```{r}
los %>%
  st_drop_geometry() %>%
  pivot_wider(names_from = timing, 
              values_from = los, 
              values_fill = 0) %>%
  filter(`During covid` > 0) %>%
  mutate(los_d = `During covid` / `Pre-covid` - 1) %>%
  left_join(foodbank_locations %>%
            transmute(OBJECTID = ID,
                      geometry),
          by = "OBJECTID") %>%
  st_as_sf() %>%
  ggplot() +
  geom_sf(data = hamilton_boundary) +
  geom_sf(aes(color = los_d,
              size = los_d)) +
  geom_sf(data = foodbank_locations,
          aes(shape = COVIDClose)) +
  scale_color_distiller(palette = "OrRd", 
                        direction = -1) +
  scale_shape_manual(values = c("Yes" = 4, "No" = 1))

@@

Plot accessibility before and during covid:
```{r}
acc_pre <- ggplot() +
  geom_sf(data = hamilton_boundary) +
  geom_sf(data = accessibility %>%
            filter(timing == "Pre-covid"),
          aes(color = accessibility)) +
  scale_color_distiller(palette = "OrRd", 
                        direction = 1)

acc_covid <- ggplot() +
  geom_sf(data = hamilton_boundary) +
  geom_sf(data = accessibility %>%
            filter(timing == "During covid"),
          aes(color = accessibility)) +
  scale_color_distiller(palette = "OrRd", 
                        direction = 1)

@@

Plot the change in accessibility by DA:
```{r}
accessibility %>%
  st_drop_geometry() %>%
  # Copy the DA identifier to the accessibility table
  left_join(dwelling_network_points_2016 %>%
              st_drop_geometry() %>%
              transmute(UID = ID, DAUID),
            by = "UID") %>%
  # Group by DA and time
  group_by(DAUID, timing) %>%
  # Calculate the accessibility by DA before and during covid
  summarize(accessibility = sum(accessibility),
            timing = first(timing),
            .groups = "drop") %>%
  # Pivot wider to calculate the differences in accessibility from pre-covid to covid
  pivot_wider(names_from = timing, 
              values_from = accessibility) %>%
  # Calculate changes in accessibility
  mutate(acc_d = `During covid` / `Pre-covid` - 1) %>%
  # Join DA geometry
  left_join(data_da_2016 %>%
            transmute(DAUID = GeoUID,
                      geometry),
          by = "DAUID") %>%
  # Convert to simple features
  st_as_sf() %>%
  # Plot
  ggplot() +
  geom_sf(data = hamilton_boundary) +
  geom_sf(aes(fill = acc_d),
          color = NA) +
  scale_fill_distiller(palette = "OrRd", 
                        direction = -1)

@@

### Pre-COVID Scenario

@@

```{r minimum-travel-time-baseline, include=FALSE}
# retrieve minimum travel time for pre-covid locations
min_ttm_car_baseline <- ttm_car %>%
  #dplyr::filter(COVIDClose == "No") %>%
  group_by(UID) %>%
  summarize(travel_time = min(travel_time),
            DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            p_car = first(p_car),
            p_transit = first(p_transit),
            p_walk = first(p_walk),
            children = first(children),
            adults = first(adults),
            seniors = first(seniors),
            .groups = "drop") %>%

  ## Calculate weighted travel time:
  mutate(weighted_travel_time = travel_time * p_car)

min_ttm_transit_baseline <- ttm_transit %>%
  #dplyr::filter(COVIDClose == "No") %>%
  group_by(UID) %>%
  summarize(travel_time = min(travel_time),
            DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            p_car = first(p_car),
            p_transit = first(p_transit),
            p_walk = first(p_walk),
            children = first(children),
            adults = first(adults),
            seniors = first(seniors),
            .groups = "drop") %>%

  ## Calculate weighted travel time:
  mutate(weighted_travel_time = travel_time * p_transit)

min_ttm_walk_baseline <- ttm_walk %>%
  #dplyr::filter(COVIDClose == "No") %>%
  group_by(UID) %>%
  summarize(travel_time = min(travel_time),
            DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            p_car = first(p_car),
            p_transit = first(p_transit),
            p_walk = first(p_walk),
            children = first(children),
            adults = first(adults),
            seniors = first(seniors),
            .groups = "drop") %>%

  ## Calculate weighted travel time:
  mutate(weighted_travel_time = travel_time * p_walk)
```

Bind the tables and label by mode:

```{r weighted-travel-time-by-mode-baseline, include=FALSE}
# Baseline analysis (pre-COVID)
## Bind the three tables and label them by mode:
min_ttm_mode_baseline <- rbind(data.frame(min_ttm_car_baseline, Mode = "Car"),
                               data.frame(min_ttm_transit_baseline, Mode = "Transit"),
                               data.frame(min_ttm_walk_baseline, Mode = "Walking"))
```

```{r aggregate-weighted-travel-times-baseline, include=FALSE}
# Baseline analysis (pre-COVID)
## Aggregate weighted travel times by mode:
min_ttm_mode_baseline <- min_ttm_mode_baseline %>%
  group_by(UID) %>%
  summarize(DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            children = first(children),
            adults = first(adults),
            seniors = first(seniors),
            weighted_travel_time = sum(weighted_travel_time)) %>%

  # add geometry
  #left_join(population_age_income %>%
  #            transmute(geometry, TAZUID),
  #          by = "TAZUID") %>%

  # calculate person-weighted hours
  mutate(wph_children = children*weighted_travel_time/60,
         wph_adults = adults*weighted_travel_time/60,
         wph_seniors = seniors*weighted_travel_time/60)
```

```{r summarize-results-by-taz-baseline, include=FALSE}
# Baseline analysis (pre-COVID)
## Summarize by TAZ and join geometry:
min_ttm_baseline_taz <- min_ttm_mode_baseline %>%
  group_by(TAZUID) %>%
  summarize(weighted_travel_time = mean(weighted_travel_time),
            wph_children = sum(wph_children),
            wph_adults = sum(wph_adults),
            wph_seniors = sum(wph_seniors)) %>%

  left_join(population_age_income %>%
              transmute(geometry, TAZUID),
            by = "TAZUID") %>%

  st_as_sf()
```

```{r}
tm_shape(min_ttm_baseline_taz) +
  tm_fill("wph_children")

tm_shape(min_ttm_baseline_taz) +
  tm_fill("wph_adults")

tm_shape(min_ttm_baseline_taz) +
  tm_fill("wph_seniors")
```

```{r weighted-travel-time-map-baseline}
# Baseline analysis (pre-COVID)
## Map weighted travel time:
ttm_map_baseline <- ggplot() +
  geom_sf(data = min_ttm_baseline_taz,
          aes(fill = weighted_travel_time),
          color = NA) +
  scale_fill_distiller(name = "Expected travel time (min)",
                       palette = "OrRd", 
                       direction = 1)

ttm_map_baseline
```

### Do it again for the during-COVID scenario:

```{r minimum-travel-time-covid, include=FALSE}
# retrieve minimum travel time during covid to sites that didnt close
min_ttm_car_covid <- ttm_car %>%
  dplyr::filter(COVIDClose == "No") %>%
  group_by(UID) %>%
  summarize(travel_time = min(travel_time),
            DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            p_car = first(p_car),
            p_transit = first(p_transit),
            p_walk = first(p_walk),
            children = first(children),
            adults = first(adults),
            seniors = first(seniors),
            .groups = "drop") %>%

  ## Calculate weighted travel time:
  mutate(weighted_travel_time = travel_time * p_car)

min_ttm_transit_covid <- ttm_transit %>%
  dplyr::filter(COVIDClose == "No") %>%
  group_by(UID) %>%
  summarize(travel_time = min(travel_time),
            DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            p_car = first(p_car),
            p_transit = first(p_transit),
            p_walk = first(p_walk),
            children = first(children),
            adults = first(adults),
            seniors = first(seniors),
            .groups = "drop") %>%

  ## Calculate weighted travel time:
  mutate(weighted_travel_time = travel_time * p_transit)

min_ttm_walk_covid <- ttm_walk %>%
  dplyr::filter(COVIDClose == "No") %>%
  group_by(UID) %>%
  summarize(travel_time = min(travel_time),
            DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            p_car = first(p_car),
            p_transit = first(p_transit),
            p_walk = first(p_walk),
            children = first(children),
            adults = first(adults),
            seniors = first(seniors),
            .groups = "drop") %>%

  ## Calculate weighted travel time:
  mutate(weighted_travel_time = travel_time * p_walk)
```

Bind the tables and label by mode:

```{r weighted-travel-time-by-mode-covid, include=FALSE}
# Baseline analysis (pre-COVID)
## Bind the three tables and label them by mode:
min_ttm_mode_covid <- rbind(data.frame(min_ttm_car_covid, Mode = "Car"),
                               data.frame(min_ttm_transit_covid, Mode = "Transit"),
                               data.frame(min_ttm_walk_covid, Mode = "Walking"))
```

```{r aggregate-weighted-travel-times-covid, include=FALSE}
# Baseline analysis (pre-COVID)
## Aggregate weighted travel times by mode:
min_ttm_mode_covid <- min_ttm_mode_covid %>%
  group_by(UID) %>%
  summarize(DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            children = first(children),
            adults = first(adults),
            seniors = first(seniors),
            weighted_travel_time = sum(weighted_travel_time)) %>%

  # add geometry
  #left_join(population_age_income %>%
  #            transmute(geometry, TAZUID),
  #          by = "TAZUID") %>%

  # calculate person-weighted hours
  mutate(wph_children = children*weighted_travel_time/60,
         wph_adults = adults*weighted_travel_time/60,
         wph_seniors = seniors*weighted_travel_time/60)
```

```{r summarize-results-by-taz-covid, include=FALSE}
# Baseline analysis (PILOT LOCATIONS ONLY)
## Summarize by TAZ and join geometry:
min_ttm_covid_taz <- min_ttm_mode_covid %>%
  group_by(TAZUID) %>%
  summarize(weighted_travel_time = mean(weighted_travel_time),
            wph_children = sum(wph_children),
            wph_adults = sum(wph_adults),
            wph_seniors = sum(wph_seniors)) %>%

  left_join(population_age_income %>%
              transmute(geometry, TAZUID),
            by = "TAZUID") %>%

  st_as_sf()
```

```{r}
tm_shape(min_ttm_covid_taz) +
  tm_fill("wph_children")

tm_shape(min_ttm_covid_taz) +
  tm_fill("wph_adults")

tm_shape(min_ttm_covid_taz) +
  tm_fill("wph_seniors")
```

```{r weighted-travel-time-map-covid}
# Baseline analysis (PILOT LOCATIONS ONLY)
## Map weighted travel time:
ttm_map_covid <- ggplot() +
  geom_sf(data = min_ttm_covid_taz,
          aes(fill = weighted_travel_time),
          color = NA) +
  scale_fill_distiller(name = "Expected travel time (min)",
                       palette = "OrRd", 
                       direction = 1)

ttm_map_covid
```

### Map Differences

Join the min travel time tables together

```{r}
min_ttm_d <- min_ttm_baseline_taz %>% 
  left_join(min_ttm_covid_taz %>%
              st_drop_geometry() %>%
              transmute(TAZUID,
                        wph_children_covid = wph_children,
                        wph_adults_covid = wph_adults,
                        wph_seniors_covid = wph_seniors), 
            by = "TAZUID") %>%
  mutate(wph_children_d = wph_children_covid / wph_children - 1,
         wph_adults_d = wph_adults_covid / wph_adults - 1,
         wph_seniors_d = wph_seniors_covid / wph_seniors - 1)

tm_shape(min_ttm_d) + 
  tm_fill("wph_children_d")

tm_shape(min_ttm_d) + 
  tm_fill("wph_adults_d")

tm_shape(min_ttm_d) + 
  tm_fill("wph_seniors_d")
```
